fdcoexist

### 2018-09-20 meta_simulations.Rmd
Put 2 different k values in meta simulations

meta_simul = function(seed_number) {
    set.seed(seed_number)
    uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                       cor_coef = 0)
    set.seed(seed_number)
    low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                         cor_coef = 0.3)

@@

    apply(all_facets, 1, function(given_row) {
        multigen(traits = all_cor[[given_row[["cor_level"]]]],
                 trait_weights = trait_scenarios[[given_row[["scenario"]]]],
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = all_compet[[given_row[["compet_status"]]]][["A"]],
                 B = all_compet[[given_row[["compet_status"]]]][["B"]],
                 d = d,
                 k = k,
                 width = all_env[[given_row[["env_width"]]]]) %>%
            landscape_df(all_cor[[given_row[["cor_level"]]]],
                         trait_scenarios[[given_row[["scenario"]]]],
                         time = 150) %>%
            inner_join(all_cor[[given_row[["cor_level"]]]] %>%
                           as.data.frame() %>%
                           rownames_to_column("species"),
                       by = "species") %>%
            group_by(patch) %>%
            mutate(rel_abund = N/sum(N)) %>%
            ungroup() %>%
            mutate(compet_status = given_row[["compet_status"]],
                   env_width     = given_row[["env_width"]],
                   cor_level     = given_row[["cor_level"]],
                   scenario      = given_row[["scenario"]],
                   seed_number = seed_number) %>%
            select(seed_number, compet_status, env_width, cor_level, scenario,
                   everything())
    }) %>%
        bind_rows() %>%
        filter(N != 0) %>%  # Take out absent species
        mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .)) %>%
        mutate(scenario = fct_relevel(scenario, names(trait_scenarios)),
               patch_optim = as.numeric(gsub("patches", "", patch))) %>%
        group_by(seed_number, compet_status, env_width, cor_level, scenario,
                 patch) %>%
        summarise(trait1_cwm  = sum(trait1_cwm),
                  trait2_cwm  = sum(trait2_cwm),
                  trait3_cwm  = sum(trait3_cwm),
                  trait1_var  = var(trait1),
                  trait2_var  = var(trait2),
                  trait3_var  = var(trait3),
                  patch_optim = unique(patch_optim))
}

@@

run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ", B)
```

@@

@@

first_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

    meta_simul(x)
}, .progress = TRUE)
tictoc::toc()

first_simuls_r2 = first_simuls %>%
    map(~.x %>%
        gather("cwm_name", "cwm_value", ends_with("cwm")) %>%
        group_by(cwm_name, add = TRUE) %>%
        do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
        ungroup() %>%
        mutate(mod_glance = lapply(mod_cwm_env, broom::glance)) %>%
        unnest(mod_glance)) %>%
    bind_rows()

first_simuls_var = first_simuls %>%
    map(~.x %>%
            select(-ends_with("cwm"))) %>%
    bind_rows() %>%
    gather("var_name", "var_value", ends_with("var"))
```

```{r}
ggplot(first_simuls_r2, aes(scenario, r.squared)) +
    geom_boxplot(aes(fill = fct_rev(cor_level)),
                 position = position_dodge(width = 0.9)) +
    facet_grid(rows = vars(env_width, compet_status), cols = vars(cwm_name),
               labeller = lab_compet_env) +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations", labels = lab_cor) +
    labs(subtitle = paste0("R2 of trait2 CWM ~ environment; ", run_char),
         x = "Scenario",
         y = expression("R"^2)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")
```

```{r}
ggplot(first_simuls_var, aes(scenario, var_value)) +
    geom_boxplot(aes(fill = fct_rev(cor_level)),
                 position = position_dodge(width = 0.9)) +
    facet_grid(rows = vars(env_width, compet_status), cols = vars(var_name),
               labeller = lab_compet_env, scales = "free_y") +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations", labels = lab_cor) +
    labs(subtitle = paste0("Trait Variance across Patches; ", run_char),
         x = "Scenario",
         y = "Trait Variance among patches") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")
```

>>>>

meta_simul = function(seed_number, given_k = k) {
    set.seed(seed_number)
    uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                       cor_coef = 0)
    set.seed(seed_number)
    low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                         cor_coef = 0.3)

@@

    apply(all_facets, 1, function(given_row) {
        multigen(traits = all_cor[[given_row[["cor_level"]]]],
                 trait_weights = trait_scenarios[[given_row[["scenario"]]]],
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = all_compet[[given_row[["compet_status"]]]][["A"]],
                 B = all_compet[[given_row[["compet_status"]]]][["B"]],
                 d = d,
                 k = given_k,
                 width = all_env[[given_row[["env_width"]]]]) %>%
            landscape_df(all_cor[[given_row[["cor_level"]]]],
                         trait_scenarios[[given_row[["scenario"]]]],
                         time = 150) %>%
            inner_join(all_cor[[given_row[["cor_level"]]]] %>%
                           as.data.frame() %>%
                           rownames_to_column("species"),
                       by = "species") %>%
            group_by(patch) %>%
            mutate(rel_abund = N/sum(N)) %>%
            ungroup() %>%
            mutate(compet_status = given_row[["compet_status"]],
                   env_width     = given_row[["env_width"]],
                   cor_level     = given_row[["cor_level"]],
                   scenario      = given_row[["scenario"]],
                   seed_number = seed_number) %>%
            select(seed_number, compet_status, env_width, cor_level, scenario,
                   everything())
    }) %>%
        bind_rows() %>%
        filter(N != 0) %>%  # Take out absent species
        mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .)) %>%
        mutate(scenario = fct_relevel(scenario, names(trait_scenarios)),
               patch_optim = as.numeric(gsub("patches", "", patch))) %>%
        group_by(seed_number, compet_status, env_width, cor_level, scenario,
                 patch) %>%
        summarise(trait1_cwm  = sum(trait1_cwm),
                  trait2_cwm  = sum(trait2_cwm),
                  trait3_cwm  = sum(trait3_cwm),
                  trait1_var  = var(trait1),
                  trait2_var  = var(trait2),
                  trait3_var  = var(trait3),
                  patch_optim = unique(patch_optim))
}

@@

```

@@

low_k = 1.15
low_k_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ", B, "; k = ",
                        low_k)
plan(multiprocess)
tictoc::tic()

low_k_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

    meta_simul(x, given_k = low_k)
}, .progress = TRUE)
tictoc::toc()

low_k_simuls_r2 = low_k_simuls %>%
    map(~.x %>%
        gather("cwm_name", "cwm_value", ends_with("cwm")) %>%
        group_by(cwm_name, add = TRUE) %>%
        do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
        ungroup() %>%
        mutate(mod_glance = lapply(mod_cwm_env, broom::glance)) %>%
        unnest(mod_glance)) %>%
    bind_rows()

low_k_simuls_var = low_k_simuls %>%
    map(~.x %>%
            select(-ends_with("cwm"))) %>%
    bind_rows() %>%
    gather("var_name", "var_value", ends_with("var"))

plot_low_k_r2 = ggplot(low_k_simuls_r2, aes(scenario, r.squared)) +
    geom_boxplot(aes(fill = fct_rev(cor_level)),
                 position = position_dodge(width = 0.9)) +
    facet_grid(rows = vars(env_width, compet_status), cols = vars(cwm_name),
               labeller = lab_compet_env) +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations", labels = lab_cor) +
    labs(subtitle = paste0("R2 of trait2 CWM ~ environment; ", low_k_run_char),
         x = "Scenario",
         y = expression("R"^2)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")
plot_low_k_r2

plot_low_k_var = ggplot(low_k_simuls_var, aes(scenario, var_value)) +
    geom_boxplot(aes(fill = fct_rev(cor_level)),
                 position = position_dodge(width = 0.9)) +
    facet_grid(rows = vars(env_width, compet_status), cols = vars(var_name),
               labeller = lab_compet_env, scales = "free_y") +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations", labels = lab_cor) +
    labs(subtitle = paste0("Trait Variance across Patches; ", low_k_run_char),
         x = "Scenario",
         y = "Trait Variance among patches") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")

plot_low_k_var
```

```{r}
high_k = 1.57
high_k_run_char = paste0("N = ", total_runs, "; A = ", A, "; B = ", B, "; k = ",
                        high_k)

@@

high_k_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

    meta_simul(x, high_k)
}, .progress = TRUE)
tictoc::toc()

high_k_simuls_r2 = high_k_simuls %>%
    map(~.x %>%
        gather("cwm_name", "cwm_value", ends_with("cwm")) %>%
        group_by(cwm_name, add = TRUE) %>%
        do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
        ungroup() %>%
        mutate(mod_glance = lapply(mod_cwm_env, broom::glance)) %>%
        unnest(mod_glance)) %>%
    bind_rows()

high_k_simuls_var = high_k_simuls %>%
    map(~.x %>%
            select(-ends_with("cwm"))) %>%
    bind_rows() %>%
    gather("var_name", "var_value", ends_with("var"))

plot_high_k_r2 = ggplot(high_k_simuls_r2, aes(scenario, r.squared)) +
    geom_boxplot(aes(fill = fct_rev(cor_level)),
                 position = position_dodge(width = 0.9)) +
    facet_grid(rows = vars(env_width, compet_status), cols = vars(cwm_name),
               labeller = lab_compet_env) +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations", labels = lab_cor) +
    labs(subtitle = paste0("R2 of trait2 CWM ~ environment; ", high_k_run_char),
         x = "Scenario",
         y = expression("R"^2)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")

plot_high_k_r2

plot_high_k_var = ggplot(high_k_simuls_var, aes(scenario, var_value)) +
    geom_boxplot(aes(fill = fct_rev(cor_level)),
                 position = position_dodge(width = 0.9)) +
    facet_grid(rows = vars(env_width, compet_status), cols = vars(var_name),
               labeller = lab_compet_env, scales = "free_y") +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations", labels = lab_cor) +
    labs(subtitle = paste0("Trait Variance across Patches; ", high_k_run_char),
         x = "Scenario",
         y = "Trait Variance among patches") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")

plot_high_k_var
```
